### 2020-12-22 Outputs/Paper/paper.Rmd
merge

---
title: "2019 Canadian Federal Election"
subtitle: "....."
author: "Yijie Zhao"
date: "22 December 2020"
abstract: |
  | ...abstract
  |
  | **Keywords:** 2019 Canadian Federal Election; Liberal; Turnout; Multilevel Regression with Post-stratification.
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

# Data

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

## ces2019 data

why cps19_votechoice as response variable? why not cps19_v_likely,cps19_vote_unlikely,cps19_vote_lean,cps19_v_advance?
sample size
other explanatory choosing

# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

# Appendix

Code and data are available at: LINK.

\newpage

# References

### 2020-12-22 Scripts/CES_2019 data cleaning.R

@@ -1,0 +1,301 @@
+#### Preamble #################################################################
+# Purpose: Prepare and clean the 2019 CES data to match cleaned census data
+# Data source: Canadian Election Study 
+# Obtained from cesR package installed from github hodgettsp/cesR
+# Author: Yijie Zhao
+# Date: 1 December 2020
+# Contact: yijie.zhao@mail.utoronto.ca
+# License: MIT
+# To save this script in folder Scripts
+# To save the half-cleaned data in folder Inputs/data_in_process, in case of 
+# unexpected crashes of Rstudio
+# To save the 2019 CES cleaned data in folder Inputs/data_for_analysis
+
+
+
+#### Workspace setup ##########################################################
+
+# Install R packages - tidyverse and labelled
+install.packages("tidyverse")
+install.packages("labelled")
+
+# Install package development tools - devtools
+install.packages("devtools")
+
+# Load R packages and devtools
+library(tidyverse)
+library(labelled)
+library(devtools)
+
+# Install cesR package
+devtools::install_github("hodgettsp/cesR")
+
+# Load cesR package
+library(cesR)
+
+
+
+#### Load data and choose variables ###########################################
+
+# As online survey contains a much larger sample size than 2019 CES phone survey
+# Call 2019 CES online survey
+get_ces("ces2019_web")
+
+# Convert variables into factors
+ces2019_web <- to_factor(ces2019_web)
+
+# There are 37822 observations of 620 variables in the original survey dataset.
+
+# Select some variables of interest
+reduced_ces2019 <- ces2019_web %>% 
+  select(cps19_votechoice,
+         cps19_citizenship, 
+         cps19_age, 
+         cps19_gender, 
+         cps19_education, 
+         cps19_employment, 
+         cps19_income_number, 
+         cps19_marital, 
+         cps19_province)
+
+# There are 37822 observations of 9 variables in the reduced survey dataset.
+
+# Save data subset reduced_ces2019 in folder Inputs/data_in_process
+write.csv(reduced_ces2019, 
+          file="Inputs/data_in_process/reduced_ces2019.csv", row.names=F)
+
+# Delete dataset ces2019_web and reduced_ces2019
+rm(ces2019_web, reduced_ces2019)
+# Use data file, reduced_ces2019.csv in the following section
+
+
+
[…]

### 2020-12-22 Scripts/Census_2016 data cleaning.R

@@ -1,0 +1,235 @@
+#### Preamble #################################################################
+# Purpose: Prepare and clean the 2016 Canadian census data 
+# Data source: Statistics Canada 2016 census program 
+# Obtained from U of T library (cited in report)
+# Author: Yijie Zhao
+# Date: 1 December 2020
+# Contact: yijie.zhao@mail.utoronto.ca
+# License: MIT
+# Prerequisites: downloaded the data from U of T library. To do that:
+## 1. Go to: http://www.chass.utoronto.ca/
+## 2. Data centre --> UofT users or http://dc.chass.utoronto.ca/myaccess.html
+## 3. Click Canadian Census, should redirect to sign in. Sign in.
+## 4. Click Public use microdata files (PUMF) - Census PUMF files.
+## 5. Choose Census of Canada, 2016 - individuals and click "Data". 
+## 6. Click download --> Customized Subset.
+## 7. Select CSV data file, data definitions for STATA.
+## 8. Select variables by clicking button. Then continue.
+## 9. Create the files, download and save.
+# To save the raw data in folder Inputs/data_raw 
+# To save this script in folder Scripts
+# To save the half-cleaned data in folder Inputs/data_in_process, in case of 
+# unexpected crashes of Rstudio
+# To save the cleaned census data in folder Inputs/data_for_analysis
+
+
+
+#### Workspace setup ##########################################################
+
+# Install R packages - tidyverse and labelled
+install.packages("tidyverse")
+install.packages("labelled")
+
+# Load R packages - tidyverse and labelled
+library(tidyverse)
+library(labelled)
+
+
+
+#### Load data and choose variables ###########################################
+
+# Since 2011, Statistics Canada started to use only one mandatory short form of
+# questionnaire and move most of questions of long form to a voluntary survey 
+# called National Household Survey. I choose the data of "Census of Canada, 
+# 2016: individual public use microdata file", the most recent census data.
+
+# Read the raw data of 2016 Canadian census
+census2016_raw <- read_csv("Inputs/data_raw/AAqA7Hod.csv")
+
+# Convert variables into factors
+census2016_raw <- to_factor(census2016_raw)
+
+# There are 930421 observations of 10 variables in the original census dataset.
+
+# Select some variables of interest
+reduced_census2016 <- census2016_raw %>% 
[…]

### 2020-12-23 Outputs/Paper/paper.Rmd
3232

@@
 ---
-title: "2019 Canadian Federal Election"
-subtitle: "....."
+title: "Liberal Might Win 31.80% of Popular Votes with 100% Turnout Rate"
 author: "Yijie Zhao"
@@
 abstract: |
-  | ...abstract
+  | Turnout rate has been always playing an important role in democratic 
+  election system. In this paper, we are going to figure out what outcome
+  would occur if every qualified voters voted in 2019 Canadian Federal election.
+  We will use multilevel regression with post-stratification techniques to 
+  estimate the vote share that Liberal would win if the turnout rate is 100%.
+  We will also discuss about the importance of turnout rate at last.
   |
-  | **Keywords:** 2019 Canadian Federal Election; Liberal; Turnout; Multilevel Regression with Post-stratification.
+  | **Keywords:** 2019 Canadian Federal Election; Liberal; Turnout; Multilevel 
+  Regression with Post-stratification.
 output: pdf_document
@@
 ```{r setup, include=FALSE}
+# Work space setup
 knitr::opts_chunk$set(echo = TRUE)
+install.packages("tidyverse")
+install.packages("labelled")
+install.packages("car")
+install.packages("lme4")
+install.packages("broom")
+install.packages("kableExtra")
+library(tidyverse)
+library(labelled)
+library(car)
+library(lme4)
+library(broom)
+library(kableExtra)
 ```
@@
 
-# Data
+# 2  Data
 
-Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)
+```{r, include=FALSE}
+# Read cleaned 2019 CES survey data
+ces_2019 <- 
+  read_csv("/cloud/project/Inputs/data_for_analysis/ces2019_clean.csv")
 
-## ces2019 data
+# Read cleaned 2016 census data
+census_2016 <- 
+  read_csv("/cloud/project/Inputs/data_for_analysis/census2016_clean.csv")
+```
 
-why cps19_votechoice as response variable? why not cps19_v_likely,cps19_vote_unlikely,cps19_vote_lean,cps19_v_advance?
-sample size
-other explanatory choosing
+In order to figure out the influence of voter turnout on the 2019 Canadian federal election, I chose two sets of data for analyzing and modeling.
+One is 2019 Canadian Election Study (CES) survey data (@citeces) and the other is 2016 Canadian census data (@citecensus).
+In this paper, I used 2019 CES data as individual level survey data, to build model for predicting the polling of popular votes.
+Meanwhile, I used 2016 Canadian census data as post-stratification data, to make better estimates by adjusting the outcomes of model prediction with the population distribution.
 
-# Model
+In the following data section, I first discussed about the key points of these two data sets in the first two parts, for example, contents of survey design and data collection.
+Then I drew some plots of each data, to make key features of these data more intuitively visualized.
 
-\begin{equation}
-Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
-\end{equation}
+## 2.1  Individual Level Survey Data
 
-Equation \@ref(eq:bayes) seems useful, eh?
+For individual-level survey data, I used the 2019 CES survey data released by Canadian Election Study in August 17, 2020.
+Canadian Election Study is a study group led by Laura Stephenson et al, focusing on the research of Canadian election activities, since 1965.
+This study group makes surveys on every election year and collect all aspects of data related to Canadian election from their target population.
+I obtained the datasets of 2019 CES survey data from loading a R package named cesR (@citecesR).
+The CES team made two modes of survey this time, one is online survey with sample size of 37,822 and the other is phone survey with sample size of 4,021.
+In this analysis paper, I chose the online survey (@citeces), because it contains a much larger sample size of data than the phone survey, which can enhance representativeness of population.
 
-Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR].
-We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.
+The population of this 2019 CES survey is all Canadian citizens and permanent residents, with age of 18 or older.
+Around the period of election, they made a two-wave online survey.
+The first wave started from September 13 to October 21, 2019, which was during the campaign period, with 37,822 interviews.
+The second wave started from October 24 to November 11, 2019, which was after the federal election, with 10,337 interviews.
+They used stratified sampling by region and sampled 37,822 respondents through Qualtrics, which provided them with the frame list of target population.
+As for the response rate and data quality, they got 37,822 responses in total for campaign period survey before the federal election, and among these responses, about 89.64% of responses are with high quality.
 
-# Results
+I chose the data of campaign period online survey as my individual level survey data.
+The first reason is that the campaign period online survey sampled much more respondents than the post election survey.
+Second, I intended to build a prediction model for voting in 2019 federal election.
+Therefore, I need a response variable which represents an intention of voting or a preference of different Canadian political parties, not a variable of voting results after election.
+
+After datasets selection, I used R (@citeR) to write scripts for cleaning this survey data.
+First, I removed all samples who did not have Canadian citizenship, which means they didn't have rights to vote in federal election.
+Among the 620 variables of this survey data, I focused on demographic variables.
+I selected some demographic variables and used them to create new categorical variables as explanatory variables for this analysis paper.
+They reason why I adjusted these original variables is because I need to make each pair of homogeneous variables exactly the same in survey data and the following census data, so that I could build prediction model by using survey data and apply model to census data successfully.
+
+The adjusted explanatory variables are showed as follows:
+
+- age_group;
+- gender;
+- education;
+- working_status;
+- income;
+- marital;
+- province
+
+I also created a new binary categorical variable named vote_Liberal, valuing 1 with "Yes" and 0 with "No".
+
+## 2.2  Post-stratification Data
+
+For post-stratification data, I used the data of "Census of Canada, 2016: individual public use microdata file" (@citecensus), which is the most recent census data.
+The 2016 Canadian census data was collected and released by Statistics Canada in 2016.
+Statistics Canada holds this census program every five years.
+I obtained the public used microdata file of 2016 census data through library website of University of Toronto.
+I visited the website of CHASS data centre and downloaded the data file of 2016 census program.
+
+The target population of this 2016 census data is people lived in Canada on the reference date, May 10, 2016.
+The frame is a list of household addresses of individuals and households.
+2016 census data collection used the wave methodology.
+There were 3 waves in total, which aimed at reminding people to complete survey and reducing the cases of non-response.
+There were three options to complete census survey, responding online, writing mailed paper questionnaire and mailing back, and contacting help line.
+In the past, there were one short mandatory questionnaire and one long voluntary questionnaire.
+Since 2011, Statistics Canada started to use only one mandatory short form and move most of questions of long form to a voluntary survey called National Household Survey.
+I chose the PUMF of 2016 census data.
+This data file was sampled in two-phase to the respondents of long form census, by systematic sampling methods.
+The total sample size is 930,421, which represents 2.7% of target population.
+
+As for the data quality of this census file, the sampling errors still exist obviously because this data file sampled from long form respondents, i.e., sample from samples.
+In this analysis paper, I assumed this census data is representative for population.
+As for non-response in census program, Statistics Canada changed the mandatory survey in 2015.
+Therefore, the response rate of 2016 census survey are extremely high, 96.6%.
+
+I used R (@citeR) to write scripts for cleaning this census data, the same as how I cleaned and prepared the survey data in the previous part.
+I adjusted demographic variables I chose to match the explanatory variables in survey data.
+The adjusted explanatory variables are showed as follows:
+
+- age_group;
+- gender;
+- education;
+- working_status;
+- income;
+- marital;
+- province
+
+## 2.3  Data Visualization
+
+After data cleaning, there are 18645 observations of 8 variables in the cleaned CES dataset and 668655 observations of 7 variables in the cleaned census dataset.
+Before building MRP model, I need to compare the differences of variable distributions of survey data and census data, in a more intuitive way.
+Therefore, I drew 7 pairs of plots for 7 explanatory variables that I had interested in, by using R
+package tidyverse (@citetidyverse) and ggplot2 (@citeggplot2).
+
+```{r, echo=FALSE}
+# Split page to 2x1 format
+par(mfrow=c(2,1))
+
+# Age distribution
+# Individual level survey data
+ces_2019 %>% ggplot(aes(x=age_group)) +
+  geom_bar(position=position_dodge(0.7), width=0.7) +
+  labs(title="Figure 1. Age Distribution of 2019 CES Survey Data",
+       caption = "Source: Canadian Election Study",
+       x="Age Group",
+       y="Number") +
+  theme(axis.text.x=element_text(angle=45,hjust=1))
+
+# Age distribution
+# post-stratification census data
+census_2016 %>% ggplot(aes(x=age_group)) +
+  geom_bar(position=position_dodge(0.7), width=0.7) +
+  labs(title="Figure 2. Age Distribution of 2016 Census Data",
+       caption = "Source: Statistics Canada",
+       x="Age Group",
+       y="Number") +
+  theme(axis.text.x=element_text(angle=45,hjust=1))
+```
+
+From Figure 2, you can find that in census data, the age groups of 18 to 29 years old and 50 to 59 years old have the largest two portion of population.
+However, comparing Figure 1 with Figure 2, the proportion of 18 to 29 year-old respondents is the smallest in survey data.
+That indicates the young people under 30 years old are under sampled in CES survey data, compared to census data.
+
+```{r, echo=FALSE}
+# Split page to 2x1 format
+par(mfrow=c(2,1))
+
+# Gender distribution
+# Individual level survey data
+ces_2019 %>% ggplot(aes(x=gender)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 3. Gender Distribution of 2019 CES Survey Data",
+       caption = "Source: Canadian Election Study",
+       x="Gender",
+       y="Number")
+
+# Gender distribution
+# post-stratification census data
+census_2016 %>% ggplot(aes(x=gender)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 4. Gender Distribution of 2016 Census Data",
+       caption = "Source: Statistics Canada",
+       x="Gender",
+       y="Number") 
+```
+
+From Figure 3 and Figure 4, it is obvious that the ratio of gender is more unbalanced in survey data than in census data.
+Female are over sampled and male are under sampled in 2019 CES survey data, compared with 2016 census data.
+
+```{r, echo=FALSE}
+# Split page to 2x1 format
+par(mfrow=c(2,1))
+
+# Education distribution
+# Individual level survey data
+ces_2019 %>% ggplot(aes(x=education)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 5. Education Distribution of 2019 CES Survey Data",
+       caption = "Source: Canadian Election Study",
+       x="Highest Degree",
+       y="Number") +
+  theme(axis.text.x=element_text(angle=45,hjust=1))
+
+# Education distribution
+# post-stratification census data
+census_2016 %>% ggplot(aes(x=education)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 6. Education Distribution of 2016 Census Data",
+       caption = "Source: Statistics Canada",
+       x="Highest Degree",
+       y="Number") +
+  theme(axis.text.x=element_text(angle=45,hjust=1))
+```
+
+From Figure 5 and Figure 6, we can figure that the distributions of respondents' highest degrees are totally different in two data sets.
+Compared to census data, people with and without high school diploma as highest degrees are both under sampled in survey data.
+Besides, people with bachelor's degree are obviously over sampled in CES survey data.
+
+```{r, echo=FALSE}
+# Split page to 2x1 format
+par(mfrow=c(2,1))
+
+# working_status distribution
+# Individual level survey data
+ces_2019 %>% ggplot(aes(x=working_status)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 7. Working Status Distribution of 2019 Survey Data",
+       caption = "Source: Canadian Election Study",
+       x="Working Status",
+       y="Number")
+
+# working_status distribution
+# post-stratification census data
+census_2016 %>% ggplot(aes(x=working_status)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 8. Working Status Distribution of 2016 Census Data",
+       caption = "Source: Statistics Canada",
+       x="working_status",
+       y="Number") 
+```
+
+From Figure 7 and Figure 8, it is showed that the distributions of whether people worked are almost identical in survey data and census data.
+The number of people that are currently not working is almost half of the number of people working by the reference date.
+
+```{r, echo=FALSE}
+# Split page to 2x1 format
+par(mfrow=c(2,1))
+
+# income distribution
+# Individual level survey data
+ces_2019 %>% ggplot(aes(x=income)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 9. Income Distribution of 2019 CES Survey Data",
+       caption = "Source: Canadian Election Study",
+       x="Annual Income",
+       y="Number") +
+  theme(axis.text.x=element_text(angle=45,hjust=1))
+
+# income distribution
+# post-stratification census data
+census_2016 %>% ggplot(aes(x=income)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 10. Income Distribution of 2016 Census Data",
+       caption = "Source: Statistics Canada",
+       x="income",
+       y="Number") +
+  theme(axis.text.x=element_text(angle=45,hjust=1))
+```
+
+From Figure 9 and Figure 10, I think people with annual income level of CAD 45,000 to $89,999 are over sampled, while other four groups of different annual income level are under sampled, relatively.
+But the income distributions of both data follow a pretty same distributed pattern.
+
+```{r, echo=FALSE}
+# Split page to 2x1 format
+par(mfrow=c(2,1))
+
+# marital distribution
+# Individual level survey data
+ces_2019 %>% ggplot(aes(x=marital)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 11. Marital Distribution of 2019 CES Survey Data",
+       caption = "Source: Canadian Election Study",
+       x="Marital Status",
+       y="Number")
+
+# marital distribution
+# post-stratification census data
+census_2016 %>% ggplot(aes(x=marital)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 12. Marital Distribution of 2016 Census Data",
+       caption = "Source: Statistics Canada",
+       x="Marital Status",
+       y="Number") 
+```
+
+From Figure 11 and Figure 12, it is showed that the distributions of whether people are currently married are almost identical in survey data and census data.
+The number of people that are currently married is twice as the number of people who are single by the reference date.
+
+```{r, echo=FALSE}
+# Split page to 2x1 format
+par(mfrow=c(2,1))
+
+# province distribution
+# Individual level survey data
+ces_2019 %>% ggplot(aes(x=province)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 13. Province Distribution of 2019 CES Survey Data",
+       caption = "Source: Canadian Election Study",
+       x="Province",
+       y="Number") +
+  theme(axis.text.x=element_text(angle=45,hjust=1))
+
+# province distribution
+# post-stratification census data
+census_2016 %>% ggplot(aes(x=province)) +
+  geom_bar(position=position_dodge(0.5), width=0.5) +
+  labs(title="Figure 14. Province Distribution of 2016 Census Data",
+       caption = "Source: Statistics Canada",
+       x="Province",
+       y="Number") +
+  theme(axis.text.x=element_text(angle=45,hjust=1))
+```
+
+From Figure 13 and Figure 14, it is showed that the distributions of which province people are currently living are almost identical in survey data and census data.
+The rank of provinces in terms of population is Ontario, Quebec, British Columbia and Alberta.
+The proportion of population in other province and territory is really small.
+
+# 3  Model
+
+After discussing the differences between distributions of each pair of explanatory variables in survey data and census data, I found it appropriate to build a logistics regression model to predict the probability that a voter would like to vote for Liberal Party in 2019 Canadian federal election, with explanatory variables of age, gender, education, working status, income, marital status and province.
+I used the 2019 CES survey data to build this model.
+However, as we all know, a single level of logistics regression model may not best fit the survey data, because there are obvious and huge differences between individuals, in terms of the 7 demographic variables; besides, some individuals also have something in common.
+Therefore, building a multilevel logistics regression model can solve this problem.
+
+First, I need to choose a region or cell to divide individuals into several groups and individuals in the same group have something in common.
+I chose province as the cell of this multilevel model for 2 reasons.
+The one reason is that the province is a sort of natural group, which is not man-made.
+The second reason is that we usually hear that some certain provinces are the traditional stronghold of a political party.
+Grouping by province can hold the traditions consistent.
+
+I built a multilevel logistics regression model as follows:
+$$\frac{p_{ij}}{1-p_{ij}}=exp(\beta_{0j}+\beta_{1j}x_{1ij}+\beta_{2}x_{2i}+
+\beta_{3}x_{3i}+\beta_{4}x_{4i}+\beta_{5}x_{5i}+\beta_{6}x_{6i}+\epsilon_{ij})$$
+with a random intercept and one random coefficient.
+
+The j represents group, i.e., province j, where j can value 1 to 11, as there are 11 provinces or territories in total.
+Then we get 11 different logistics regression model with different intercept term $\beta_{0}$ and coefficient $\beta_{1}$ for 11 provinces.
+The i represents the i'th observations in group j.
+The fraction $\frac{p_{ij}}{1-p_{ij}}$ represents the odds and $x_{2-6}$ represents gender, age group, education, working status, income and marital status respectively.
+And the $\epsilon$ represents error term.
+
+I used R package lme4 (@citelme4) to build the MR model and summarize the model outputs.
+
+```{r, include=FALSE}
+# Build multilevel logistics regression model
+model_mr <- glmer(
+  vote_Liberal~(1+gender|province)+age_group+education+working_status+income+
+    marital, data=ces_2019, family=binomial)
+
+# Summarize model outputs
+summary(model_mr)
+```
+
+```{r, include=FALSE}
+coef(model_mr)
+```
+
+Given the R outputs of modeling, one of the multilevel logistics regression models are showed as follows.
+
+for example, the regression model of province Alberta is:
+$$\frac{p_{i}}{1-p_{i}}=exp(-1.3397905+0.13980249Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+# 4  Results
+
+After building the multilevel regression model, next step is post stratification.
+I applied the model to predict the proportions that each individual in census data may vote Liberal Party in 2019 Canadian federal election.
+I assumed the census data represents the overall Canadian qualified voters, and based on that assumption, the overall proportions that voters would like to vote Liberal equals the overall vote share or polling of Liberal in 2019 election, if every qualified voters participate in voting.
+
+```{r, include=FALSE}
+# post-stratification
+# apply the MR model to predict y with post-stratification census data
+# predict probs for each individual of census data
+probs <- predict(model_mr,
+             census_2016[,c("age_group","gender","education","working_status",
+                            "income","marital","province")], type="response")
+
+# combine column of probs with census dataset
+census_2016 %>% cbind(census_2016, probs)
+
+# calculate mean of probs for each province observations of census data
+vote_Liberal_census <- census_2016 %>% group_by(province) %>%
+  summarise(proportion1=n()*mean(probs)/nrow(census_2016))
+```
+
+```{r, include=FALSE}
+# probs of ces data
+probs2 <- predict(model_mr,ces_2019, type="response")
+# calculate mean of probs for each province observations of survey data
+vote_Liberal_survey <- ces_2019 %>% group_by(province) %>%
+  summarise(proportion2=n()*mean(probs2)/nrow(ces_2019))
+```
+
+```{r, include=FALSE}
+# combine two proportions of each dataset
+vote_Liberal_est <- cbind(vote_Liberal_census, vote_Liberal_survey)
+vote_Liberal_est[,-3]  # delete overlapped column
+```
+
+```{r, include=FALSE}
+# calculate overall vote share for Liberal
+sum(vote_Liberal_est$proportion1)
+sum(vote_Liberal_est$proportion2)
+```
+
+The predicted overall voting share for Liberal Party is 0.3180081, which is about 31.80% if the turnout rate is 100% that every qualified voters vote in 2019 Canadian Federal Election.
 
@@
 
-## First discussion point
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
+# Weaknesses and next steps
 
@@
 
-Code and data are available at: LINK.
-
-\newpage
+Code and data are available at: https://github.com/JessieZ32/2019_CA_election.
 

### 2020-12-23 Outputs/Paper/paper.Rmd
35366

@@
 date: "22 December 2020"
-abstract: |
-  | Turnout rate has been always playing an important role in democratic 
-  election system. In this paper, we are going to figure out what outcome
-  would occur if every qualified voters voted in 2019 Canadian Federal election.
-  We will use multilevel regression with post-stratification techniques to 
-  estimate the vote share that Liberal would win if the turnout rate is 100%.
-  We will also discuss about the importance of turnout rate at last.
-  |
-  | **Keywords:** 2019 Canadian Federal Election; Liberal; Turnout; Multilevel 
-  Regression with Post-stratification.
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
+  pdf_document: default
 bibliography: references.bib
@@
 
+# Abstract
+
+Turnout rate has been always playing an important role in democratic election system.
+In this paper, we are going to figure out what outcome would occur if every qualified voters voted in 2019 Canadian Federal election.
+We will use multilevel regression with post-stratification techniques to estimate the vote share that Liberal would win if the turnout rate is 100%.
+We will also discuss about the importance of turnout rate at last.
+
+**Keywords:** Federal Election; Liberal; Turnout; Multilevel Regression with Post-stratification.
+
 # Introduction
+
+In 2019 Canadian federal election, Trudeau won his re-election and Liberal Party continued to be the party in power.
+However, even though the Liberal has won the federal election, they did not achieve a complete victory.
+They won less vote share of popular votes than the Conservative.
+Also, they did not won majority seats.
+The end result was that the Liberal party formed a minority government.
+If the turnout rate was 100% in 2019 Canadian federal election, will the results be different for Liberal?
+
+In this paper, I use two sets of data, one is 2019 CES survey data, which is completely about the 2019 Canadian federal election; the other is 2016 Canadian census data, which should be representative enough to represent the population of Canada.
+I will first load and clean these two datasets, and choose some demographic variables that I think matters the vote intention of individuals.
+I will talk about the source, survey design and import features of these two datasets in the data section.
+I will also draw some plots of same variables in different dataset to compare their distributions.
+In the model section, I will use MRP technique to build a multilevel logistics regression model based on the 2019 CES survey data and then apply this model to predict the vote intention of individuals in census data.
+I will compare the results with 2019 election results.
+At last, I will discuss further more about the use of MRP and the importance of turnout rate for democratic election system.
+Also, I will think about the weakness of data and model, to try to find which
+works can be improved in the future.
 
@@
 ```{r, echo=FALSE}
-# Split page to 2x1 format
-par(mfrow=c(2,1))
 

### 2020-12-24 Outputs/Paper/paper.Rmd
merge

@@
 date: "22 December 2020"
-output:
-  html_document:
-    df_print: paged
-  pdf_document: default
+output: html_document
 bibliography: references.bib
@@
 install.packages("lme4")
-install.packages("broom")
-install.packages("kableExtra")
 library(tidyverse)
@@
 library(lme4)
-library(broom)
-library(kableExtra)
 ```
@@
 
-# Introduction
+# 1  Introduction
 
@@
 
-After datasets selection, I used R (@citeR) to write scripts for cleaning this survey data.
+After datasets selection, I used R (@citeR) and R package tidyverse (@citetidyverse), labelled (@citelabelled) to write scripts for cleaning this survey data.
 First, I removed all samples who did not have Canadian citizenship, which means they didn't have rights to vote in federal election.
@@
 
+Besides, as the census data was collected in 2016, I should assume that there are no remarkable differences of the target population, from 2016 to 2019, in terms of population and other variables I listed in data section.
+
 ## 2.3  Data Visualization
@@
 Before building MRP model, I need to compare the differences of variable distributions of survey data and census data, in a more intuitive way.
-Therefore, I drew 7 pairs of plots for 7 explanatory variables that I had interested in, by using R
-package tidyverse (@citetidyverse) and ggplot2 (@citeggplot2).
+Therefore, I drew 7 pairs of plots for 7 explanatory variables that I had interested in, by using R package tidyverse (@citetidyverse) and ggplot2 (@citeggplot2).
 
@@
   theme(axis.text.x=element_text(angle=45,hjust=1))
+```
 
+```{r, echo=FALSE}
 # Age distribution
@@
        y="Number") 
+```
 
+```{r, echo=FALSE}
 # Gender distribution
@@
   theme(axis.text.x=element_text(angle=45,hjust=1))
+```
 
+```{r, echo=FALSE}
 # Education distribution
@@
        y="Number") 
+```
 
+```{r, echo=FALSE}
 # working_status distribution
@@
   theme(axis.text.x=element_text(angle=45,hjust=1))
+```
 
+```{r, echo=FALSE}
 # income distribution
@@
        y="Number")
+```
 
+```{r, echo=FALSE}
 # marital distribution
@@
   theme(axis.text.x=element_text(angle=45,hjust=1))
+```
 
+```{r, echo=FALSE}
 # province distribution
@@
 
-for example, the regression model of province Alberta is:
+(1) model of Alberta
 $$\frac{p_{i}}{1-p_{i}}=exp(-1.3397905+0.13980249Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(2) model of British Columbia
+$$\frac{p_{i}}{1-p_{i}}=exp(-0.5582058-0.03699328Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(3) model of Manitoba
+$$\frac{p_{i}}{1-p_{i}}=exp(-0.4765806-0.05545706Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(4) model of New Brunswick
+$$\frac{p_{i}}{1-p_{i}}=exp(-0.1352459-0.13266754Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(5) model of Newfoundland and Labrador
+$$\frac{p_{i}}{1-p_{i}}=exp(0.2752678-0.22552643Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(6) model of Northern Canada
+$$\frac{p_{i}}{1-p_{i}}=exp(-0.1717145-0.12441829Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(7) model of Nova Scotia
+$$\frac{p_{i}}{1-p_{i}}=exp(0.1865177-0.20545102Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(8) model of Ontario
+$$\frac{p_{i}}{1-p_{i}}=exp(-0.1498536-0.12936326Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(9) model of Prince Edward Island
+$$\frac{p_{i}}{1-p_{i}}=exp(0.1459720-0.19627950Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(10) model of Quebec
+$$\frac{p_{i}}{1-p_{i}}=exp(-0.3117680-0.09273796Male_i+0.1205704Age_{30-39}\\+
+0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
+-0.1890274Income_{200k+}-0.2542376Income_{45k-89k}-0.1612432Income_{90k-139k}\\
+-0.3161805Income_{45k-}+0.177598Marital_{single})$$
+
+(11) model of Saskatchewan
+$$\frac{p_{i}}{1-p_{i}}=exp(-1.5435324+0.18588925Male_i+0.1205704Age_{30-39}\\+
 0.1325729Age_{40-49}+0.1432926Age_{50-59}+0.3260491Age_{60-69}+0.2933324Age_{70+}\\-0.4084843Degree_{college}+0.03401339Degree_{grad}-0.5207438Degree_{highschool}\\-0.6417416Degree_{NoHighschool}-0.3002453Degree_{someCollege}-0.03590807Working\\
@@
 After building the multilevel regression model, next step is post stratification.
-I applied the model to predict the proportions that each individual in census data may vote Liberal Party in 2019 Canadian federal election.
+By using R package car (@citecar), I applied the model to predict the proportions that each individual in census data may vote Liberal Party in 2019 Canadian federal election.
 I assumed the census data represents the overall Canadian qualified voters, and based on that assumption, the overall proportions that voters would like to vote Liberal equals the overall vote share or polling of Liberal in 2019 election, if every qualified voters participate in voting.
@@
 # combine column of probs with census dataset
-census_2016 %>% cbind(census_2016, probs)
-
-# calculate mean of probs for each province observations of census data
-vote_Liberal_census <- census_2016 %>% group_by(province) %>%
-  summarise(proportion1=n()*mean(probs)/nrow(census_2016))
+census_data <- cbind(census_2016, probs)
 ```
@@
 ```{r, include=FALSE}
-# probs of ces data
-probs2 <- predict(model_mr,ces_2019, type="response")
-# calculate mean of probs for each province observations of survey data
-vote_Liberal_survey <- ces_2019 %>% group_by(province) %>%
-  summarise(proportion2=n()*mean(probs2)/nrow(ces_2019))
+# calculate mean of probs for each province observations of census data
+vote_Liberal_province <- census_data %>% group_by(province) %>%
+  summarise(proportion=mean(probs, na.rm=TRUE))
 ```
 
+The table below shows the estimated vote share of each province level for Liberal party, if every qualified voters have voted in 2019 Canadian Federal election.
+
+| Table 1. Est. vote share per province  |
+| province                  | vote share | 
+| :------------------------ | :--------: |
+| Alberta                   | 16.70%	   | 
+| British Columbia          | 28.66%     | 
+| Manitoba	                | 29.06%     |	
+| New Brunswick	            | 35.27%     |	
+| Newfoundland and Labrador	| 44.04%     |	
+| Northern Canada	          | 34.08%     |	
+| Nova Scotia	              | 42.86%     |	
+| Ontario	                  | 36.59%     |	
+| Prince Edward Island	    | 41.27%     |	
+| Quebec                    | 32.71%     |
+| Saskatchewan              | 13.81%     |
+
+From the Table 1, we can see that Newfoundland and Labrador, Nova Scotia and Prince Edward Island are the top 3 in terms of vote share for Liberal party, which are over 40%.
+The performance in Ontario, New Brunswick, Northern Canada and Quebec are not bad, which are between 30% and 40%.
+However, Liberal would win small proportion of popular vote in Saskatchewan and Alberta, which are both below 20%.
+Especially in Saskatchewan, the vote share of Liberal would be as low as 13.81%.
+
+Then we calculate the overall popular vote share of Liberal through introducing the weighted average of population of each province to population of Canada. The formula is:
+$$\hat{Y}_{PS}=\frac{\sum_{j} N_{j}\hat{y_j}}{\sum_{j} N_{j}}$$
+The $$\hat{Y}_{PS}$$ represents the expected overall winning rate of popular vote for Liberal.
+The $$N_{j}$$ represents the weight of number of voters in province j to aggregate level of voters in Canada.
+The $$\hat{y_j}$$ represents the expected winning rate of popular vote for Liberal in province j.
+And the j indicates which province it is.
+
 ```{r, include=FALSE}
-# combine two proportions of each dataset
-vote_Liberal_est <- cbind(vote_Liberal_census, vote_Liberal_survey)
-vote_Liberal_est[,-3]  # delete overlapped column
+# calculate mean of probs for each province observations of census data
+vote_Liberal_census <- census_data %>% group_by(province) %>%
+  summarise(proportion1=(n()*mean(probs)/nrow(census_data)))
+
+# calculate overall vote share for Liberal
+sum(vote_Liberal_est$proportion1)
 ```
 
-```{r, include=FALSE}
-# calculate overall vote share for Liberal
-sum(vote_Liberal_est$proportion1)
-sum(vote_Liberal_est$proportion2)
-```
+Using R to sum the vote share of each province in Table 1, we can conclude that the predicted overall vote share for Liberal Party is about 31.80%, if the turnout rate is 100%, which means every qualified voters had voted in 2019 Canadian Federal Election.
 
-The predicted overall voting share for Liberal Party is 0.3180081, which is about 31.80% if the turnout rate is 100% that every qualified voters vote in 2019 Canadian Federal Election.
+# 5  Discussion
 
-# Discussion
+## 5.1  Discussion over Results
 
-# Weaknesses and next steps
+Through the analysis above, the technique I used, which is the multilevel logistics regression model with post-stratification, indicates two results.
+The first one is that Liberal might have won 31.80% of popular vote if every qualified voters had voted in 2019 Canadian Federal Election.
+The second is that Liberal might win a lot in Newfoundland and Labrador, Nova Scotia, Prince Edward Island and Ontario, under the same circumstance, which is 44.04%, 42.86%, 41.27% and 36.59% respectively.
+
+As for the overall vote share of Liberal, Liberal actually won 33.10% of popular vote in the federal election last year, 1.3% higher than the estimated rate.
+That indicates that Liberal might win less if "everyone" have participated.
+That is to say, many people who missed voting last year are considered not in favor of Liberal Party.
+
+As for the vote share of Liberal in province level, I expect that Ontario is the stronghold of Liberal Party, because Liberal might win a high rate of popular vote if "everyone" voted, and also Ontario has the largest population and the most federal election districts.
+And I expect that Alberta and Saskatchewan are the strongholds of Liberal's competitors, because the Table 1 shows low vote share of Liberal in these two provinces, which can be proved by the historical data of election results in these two provinces.
+The actual results of popular vote for Liberal in each province are showed in the following table.
+
+| Table 2. 2019 vote share per province                   |
+| province                  | vote share | Gains & losses |
+| :------------------------ | :--------: | :------------: |
+| Alberta                   | 13.10%	   | - 3.60%        |
+| British Columbia          | 26.10%     | - 2.56%        |
+| Manitoba	                | 26.20%     | - 2.80%	      |
+| New Brunswick	            | 37.60%     | + 2.33%	      |
+| Newfoundland and Labrador	| 44.70%     | + 0.66%        |
+| Northern Canada	          | 34.08%     | + 1.22%	      |
+| Nova Scotia	              | 41.10%     | - 1.46%	      |
+| Ontario	                  | 41.40%     | + 4.81%	      |
+| Prince Edward Island	    | 43.60%     | + 2.33%	      |
+| Quebec                    | 34.20%     | + 1.49%        |
+| Saskatchewan              | 11.60%     | - 2.21%        |
+
+The "+" symbol in column "Gains & losses" represents Liberal won more in the corresponding province in the actual 2019 election.
+And the "-" symbol is the opposite.
+Comparing the vote share in table 2 with table 1, I find that if the turnout rate is 100%, Liberal might win more popular vote in 5 provinces, Alberta, BC, Manitoba, Nova Scotia and Saskatchewan.
+Except for Nova Scotia, other 4 provinces are the traditional strongholds of its competitor, Conservative.
+If "everyone" had voted, Liberal might win less in other 6 provinces or territories.
+Especially in its No.1 traditional stronghold, Ontario, Liberal might lose 4.81% more with 100% turnout in the election.
+In other word, there is a higher participation rate of voters who are in favor of Liberal in its stronghold, compared to with other parties' supporters, which makes sense.
+
+## 5.2  Weaknesses and Next Steps
+
+There exist many weaknesses of this paper.
+First, it's the problem of data.
+2019 CES survey data is fine to be less representative in a way.
+However, the census data might not be as representative as I expect.
+The aim of MRP model is trying to reduce the biases that less representative survey data makes with the step of post-stratification.
+That means we need a sufficiently representative data to represent the target population.
+As the census data I used is also sampled from the 2016 Canadian census data by Statistics Canada, it will increase the biases and reduce the representativeness anyway, no matter how fittable the sampling method they used is.
+Moreover, the census data I used were obtained through the 2016 Canadian census program held by Statistics Canada.
+The data can be considered out of time, even though I have made an assumption of no big difference about data of population from 2016 to 2019.
+The importance of data freshness can not be ignored.
+
+Second, it's about modeling.
+I used a logistics regression model as the model of individual level.
+The response variable is a binary categorical variable, with value 1 and 0, i.e., voting Liberal or not.
+Other than the two-party mode of US federal election, there are more than seven political parties as candidates in Canadian federal election.
+Among those parties, 4 parties are competitive, which is reflected by the number of seats that these 4 parties have.
+So, simply distinguishing the vote intention to 2 categories seems not so reasonable.
+
+Thus, for the future work, I will improve on these two aspects.
+First, I need to find a more representative dataset for year 2019.
+The questionnaire of 2021 Canadian census program has been published in July, 2020.
+Respondents will answer most of the questions based on their own situation in 2019.
+That will be really suitable to use as post-stratification data.
+Second, next time I can build a more complicated and appropriate individual-level model for the first step of MRP.
+For example, I can build a nominal logistics regression model with response variable that contains at least 3 categories.
+Using this model, I can define response variable as parties that people prefer to vote in 2019 federal election, which contains 8 categories (7 parties and others like independent candidates).
+Therefore, I can not only estimate the popular vote share of each party in different level, but also the federal election districts that each party might win.
+For the latter, I can estimate the
+vote share of each party in each Canadian federal election districts, and based on the rule of winner-take-all, estimate the number of districts that each party might win; in other words, the number of seats in the House of Commons to the Canadian Parliament.
+That is to say, I can predict which party might be in power and which kind of government might be formed (majority or minority) after election, if the turnout rate were 100% in 2019 Canadian federal election.
 

### 2020-12-30 Outputs/Paper/paper.Rmd
try to knit again
try to knit again. succeed!

@@
 date: "22 December 2020"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 bibliography: references.bib
@@
 # calculate overall vote share for Liberal
-sum(vote_Liberal_est$proportion1)
+sum(vote_Liberal_census$proportion1)
 ```
